Digital History in Finland, 1488-1828

### 2016-07-04 inst/examples/manuscript-krakow.Rmd
ok

```{r polev1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
# TITLE COUNT
sel.places = c("Stockholm", "Uppsala", "Lund", "Greifswald", "Turku")
sel.years = c(1760, 1780)

>>>>

```{r polev1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="280px", fig.show="hold"}
# TITLE COUNT
sel.places = c("Stockholm", "Uppsala", "Lund", "Greifswald", "Turku")
sel.years = c(1760, 1780)
